Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2015-11-26 ijar-npb-ms.tex
survival signature intro by Frank

Based on expert assumptions for component failure distribution and component test data,
we make predictive inference for a system with components that are exchangeable
with the test components by calculating the system reliability function $\Rsys(t) = P(\Tsys > t)$.
Considering a discrete grid of time points $\{t_1, \ldots, \tmax\}$,
naturally a Bayesian model for the functioning probability at each time point arises.
To account for uncertainty in the choice of prior and due to the inherent issue with prior-data conflict,
we propose an imprecise or interval probability approach
based on sets of prior distributions defined through sets of canonical parameters.

Our method produces a set of discrete system reliability functions,
or, for each time point $t$, an interval for the system survival probability
that appropriately reflects uncertainty due to vague prior information, the amount of test data, and prior-data conflict.

@@

\section{Survival Signature}

The survival signature allows for straightforward computation of system reliability
for systems with complex layouts and multiple component types.
It separates the (time-invariant) system structure from the time-dependent failure probabilities of components.

Can be seen as applying the law of total probability by partitioning
according to the number of components of type $k$ functioning at time $t$,
denoted by $C^k_t \in \{0, 1, \ldots, l_k, \ldots, m_k\}$:
\begin{align*}
P(\Tsys > t)
 &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} P(\Tsys > t \mid C^1_t = l_1,\ldots, C^K_t = l_K)
                                                 P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \\
 &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K)
                                                 \prod_{k=1}^K P(C^k_t = l_k) \,.
\end{align*}

@@

>>>>

The survival signature allows for straightforward computation of system reliability
for systems with complex layouts and multiple component types.
It separates the (time-invariant) system structure from the time-dependent failure probabilities of components,
by partitioning the event $\Tsys > t$ according to the number of components of type $k$ functioning at time $t$,
denoted by $C^k_t \in \{0, 1, \ldots, l_k, \ldots, m_k\}$, and applying the law of total probability:
\begin{align*}
P(\Tsys > t)
 &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} P(\Tsys > t \mid C^1_t = l_1,\ldots, C^K_t = l_K)
                                                 P\Big( \bigcap_{k=1}^K \{ C^k_t = l_k\} \Big) \\
 &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \Phi(l_1, \ldots, l_K)
                                                 \prod_{k=1}^K P(C^k_t = l_k) \,.
\end{align*}

Based on expert assumptions for component failure distribution and component test data,
we make predictive inference for a system with components that are exchangeable
with the test components by calculating the system reliability function $\Rsys(t) = P(\Tsys > t)$.
Considering a discrete grid of time points $\{t_1, \ldots, \tmax\}$,
naturally a Bayesian model for the functioning probability at each time point arises.
To account for uncertainty in the choice of prior and due to the inherent issue with prior-data conflict (see Section~***),
we propose an imprecise or interval probability approach
based on sets of prior distributions defined through sets of canonical parameters.
This approach also allows to adequately model weak or partial prior information.
Especially prior near ignorance can be modelled much more meaningfully than through usual so-called noninformative priors.

Our method produces a set of discrete system reliability functions,
or, for each time point $t$, an interval for the system survival probability,
that appropriately reflects uncertainty due to vague prior information, the amount of test data, and prior-data conflict.

@@

The paper is organised as follows.
In Section~\ref{sec:survsign}, we describe ***

\section{Survival Signature}
\label{sec:survsign}

In mathematical theory of reliability, the main focus is on the functioning of a system given the functioning, or not, 
of its components and the structure of the system. The mathematical concept which is central to this theory is the 
\emph{structure function} \citep{BP75}. For a system with $m$ components, let state vector 
$\underline{x} = (x_1,x_2,\ldots,x_m) \in \{0,1\}^m$, with $x_i=1$ if the $i$th component functions 
and $x_i=0$ if not. The labelling of the components is arbitrary but must be fixed to define $\underline{x}$. 
The structure function $\phi : \{0,1\}^m \rightarrow \{0,1\}$, defined for all possible $\underline{x}$, takes 
the value 1 if the system functions and 0 if the system does not function for state vector $\underline{x}$. 
Most practical systems are coherent, which means that $\phi(\underline{x})$ 
is non-decreasing in any of the components of $\underline{x}$, so system functioning cannot be improved by worse performance 
of one or more of its components. The assumption of coherent systems is also convenient from the perspective of uncertainty
quantification for system reliability. It is further logical to assume that $\phi(\underline{0})=0$ and $\phi(\underline{1})=1$, 
so the system fails if all its components fail and it functions if all its components function.

For larger systems, working with the full structure function may be complicated, and one may particularly
only need a summary of the structure function in case the system has exchangeable components of one or more
types. We use the term `exchangeable components' to indicate that the failure times of the components in the system
are exchangeable \citep{DF74}. \citet{2012:survsign} introduced such a summary,
called the \emph{survival signature}, 
to facilitate reliability analyses for systems with multiple types of components. In case of just a single type of components, 
the survival signature is closely related to the system signature \citep{Sa07}, which is well-established and the topic of many
research papers during the last decade. However, generalization of the signature to systems with
multiple types of components is extremely complicated (as it involves ordering order statistics of different
distributions), so much so that it cannot be applied to most practical systems. In addition to the 
possible use for such systems, where the benefit only occurs if there are multiple components of the 
same types, the survival signature is arguably also easier to interpret than the signature.

Consider a system with $K\ge 1$ types of components, with $m_k$ components of type $k \in \{1,\ldots,K\}$ and 
$\sum_{k=1}^K m_k = m$. Assume that the random failure times of components of the same type are exchangeable \citep{DF74}.
Due to the arbitrary ordering of the components in the state vector, components of the same type can be grouped together, 
leading to a state vector that can be written as 
$\underline{x} = (\underline{x}^1,\underline{x}^2,\ldots,\underline{x}^K)$, with 
$\underline{x}^k = (x^k_1,x^k_2,\ldots,x^k_{m_k})$ the sub-vector representing the states of the components of type $k$.

The \emph{survival signature} for such a system, denoted by $\Phi(l_1,\ldots,l_K)$, with $l_k=0,1,\ldots,m_k$ 
for $k=1,\ldots,K$, is defined as the probability for the event that the system functions given that \emph{precisely} $l_k$ of its 
$m_k$ components of type $k$ function, for each $k\in \{1,\ldots,K\}$ \citep{2012:survsign}. 
There are $\binom{m_k}{l_k}$ state vectors $\underline{x}^k$ with $\sum_{i=1}^{m_k} x^k_i = l_k$. Let $S^k_{l_k}$ 
denote the set of these state vectors for components of type $k$ and let $S_{l_1,\ldots,l_K}$ denote the set of 
all state vectors for the whole system for which $\sum_{i=1}^{m_k} x^k_i = l_k$, $k=1,\ldots,K$. Due to the 
exchangeability assumption for the failure times of the $m_k$ components of type $k$, all the state vectors 
$\underline{x}^k \in S^k_{l_k}$ are equally likely to occur, hence \citep{2012:survsign}
\begin{align}
\label{eq:surv-sig}
\Phi(l_1,\ldots,l_K)
 &= \left[ \prod_{k=1}^K \binom{m_k}{l_k}^{-1} \right] \times \sum_{\underline{x} \in S_{l_1,\ldots,l_K}} \phi(\underline{x})\,.
\end{align}

Let $C^k_t \in \{0,1,\ldots,m_k\}$ denote the number of components of type $k$ in the system that function at time $t>0$.
Then, for system failure time $\Tsys$,
\begin{align*}
P(\Tsys > t) &= \Rsys(t) = \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K}  \Phi(l_1,\ldots,l_K) P\Big(\bigcap_{k=1}^K \{C^k_t = l_k\}\Big)\,.
\end{align*}
It should be emphasized that when using the survival signature,
there are no restrictions on dependence of the failure times of components of different types,
as the probability $P(\bigcap_{k=1}^K \{C^k_t = l_k\})$ can take any form of dependence into account,
for example one can include common-cause failures quite straightforwardly into this approach \citep[see][]{CCM15}.
However, there is a substantial simplification
if one can assume that the failure times of components of different types are independent,
and even more so if one can assume that the failure times of components of type $k$ 
are conditionally independent and identically distributed with CDF $F_k(t)$.
With these assumptions, we get
\begin{align*}
\Rsys(t) &= \sum_{l_1=0}^{m_1} \cdots \sum_{l_K=0}^{m_K} \left[ \Phi(l_1,\ldots,l_K)
            \prod_{k=1}^K \left( \binom{m_k}{l_k} [F_k(t)]^{m_k-l_k} [1-F_k(t)]^{l_k} \right) \right]\,.
\end{align*}

The main advantage of the survival signature, in line with this property of the signature for systems with a single type of 
components \citep{Sa07}, is that the information about the system structure is fully 
separated from the information about functioning of the components, which simplifies related statistical inference as well as
considerations of optimal system design. In particular for study of system reliability over time, with the structure of the system, 
and hence the survival signature, not changing, this separation also enables relatively straightforward statistical inferences.

There are several relatively straightforward generalizations of the use of the survival signature.
The probabilities for the numbers of functioning components can be generalized to lower and upper probabilities,
as e.g.\ done by \citet{CCMA14} within the nonparametric predictive inference (NPI) framework of statistics \citep{Co11},
where lower and upper probabilities for the events $C_k = l_k$
are inferred from test data on components of the same types as those in the system.
This is an approach that is also followed in the current paper, but with the use of generalized Bayesian inference instead of NPI.
***This step is less trivial here as we must ensure to have probability distributions for these events,
thus summing to one over $l_k=0,1,\ldots,m_k$ for each type $k$.
***covered because of parametric distribution, min and max over parameter sets (see section 6)***
***For coherent systems this is not very complicated due to the monotonicity of the survival signature,
see \citet{CCMA14} where the method for dealing with imprecision on the random quantities $C_k$ is presented.***
Recently, \citet{CCM16} suggested the generalization of the structure function from a binary function to a probability,
to reflect uncertainty about system functioning for known states of its components.
A further suggestion was to generalize this to lower and upper structure functions,
within the theory of imprecise probability \citep{itip,CU11}.
These suggestions are also easy to incorporate into system reliability with the use of the survival signature,
which in the latter case also becomes an imprecise probability.

The survival signature is a powerful but rather basic concept.
As such, further generalizations are conceptually easy,
for example one can straightforwardly generalize the survival signature to multi-state systems
such that it again summarizes the structure function
in a manner that is sufficient for a range of uncertainty quantifications for the system reliability.

@@

Upscaling the survival signature to large real-world systems and networks, consisting of thousands of components, is a major challenge.
However, even for such systems the fact that one only needs to derive the survival signature once for a system is an advantage,
and also the monotonicity of the survival signature for coherent systems is very useful if one can only derive it partially.
